---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clidatajp

<!-- badges: start -->
<!-- badges: end -->

The goal of clidatajp is to provide climate data from Japan Meteorological Agency ('JMA').
You can also download climate data from 'JMA'. 

## Installation

You can install the development version of clidatajp from [GitHub](https://github.com/) with:
You can see climate data directly from 'JMA' ( https://www.data.jma.go.jp/gmd/cpd/monitor/nrmlist/ ). 

``` r
  # CRAN
install.packages("clidatajp")

  # development
  # install.packages("devtools")
devtools::install_github("matutosi/clidatajp")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(clidatajp)
library(tidyverse)

  # show station information and link
data(station_links)
station_links %>%
  dplyr::mutate("station" := stringi::stri_unescape_unicode(station))

  # show climate data
data(japan_climate)
japan_climate %>%
  dplyr::mutate_if(is.character, stringi::stri_unescape_unicode)

data(world_climate)
world_climate %>%
  dplyr::mutate_if(is.character, stringi::stri_unescape_unicode)

  # download climate data
station_links %>%
  `$`("url") %>%
  `[[`(1) %>%
  download_climate()
```

## Citation

Toshikazu Matsumura (2022) Tools for download climate data from Japan Meteorological Agency with R. https://github.com/matutosi/clidatajp/.
