---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clidatajp

<!-- badges: start -->
<!-- badges: end -->

The goal of clidatajp is to provide climate data from Japan Meteorological Agency ('JMA').
Data was downloaded from 'JMA' and edited. 
You can also download climate data from 'JMA'. 

## Installation

You can install the development version of clidatajp from [GitHub](https://github.com/).
You can see climate data directly from 'JMA' ( https://www.data.jma.go.jp/gmd/cpd/monitor/nrmlist/ ). 

``` r
  # CRAN
install.packages("clidatajp")

  # development
  # install.packages("devtools")
devtools::install_github("matutosi/clidatajp")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(clidatajp)
library(tidyverse)

  # show station information and link
data(station_links)
station_links %>%
  dplyr::mutate("station" := stringi::stri_unescape_unicode(station))

  # show climate data
data(japan_climate)
japan_climate %>%
  dplyr::mutate_if(is.character, stringi::stri_unescape_unicode)

data(world_climate)
world_climate %>%
  dplyr::mutate_if(is.character, stringi::stri_unescape_unicode)

  # download climate data
station_links %>%
  `$`("url") %>%
  `[[`(1) %>%
  download_climate()
```

## Plot

Clean up data before drawing plot. 

```{r clean_data}
climate <- 
  dplyr::bind_rows(world_climate, japan_climate) %>%
  dplyr::mutate_if(is.character, stringi::stri_unescape_unicode)  %>%
  dplyr::group_by(station) %>%
  dplyr::filter(sum(is.na(temperature), is.na(precipitation)) == 0) %>%
  dplyr::filter(period != "1991-2020" | is.na(period))

climate <- 
  climate %>%
  dplyr::summarise(temp = mean(as.numeric(temperature)), prec = sum(as.numeric(precipitation))) %>%
  dplyr::left_join(dplyr::distinct(dplyr::select(climate, station:altitude))) %>%
  dplyr::left_join(tibble::tibble(NS = c("S", "N"), ns = c(-1, 1))) %>%
  dplyr::left_join(tibble::tibble(WE = c("W", "E"), we = c(-1, 1))) %>%
  dplyr::group_by(station) %>%
  dplyr::mutate(lat = latitude * ns, lon = longitude * we)
```

Draw a world map with temperature. 

```{r temperature}
climate %>%
  ggplot(aes(lon, lat, colour = temp)) +
    scale_colour_gradient2(low = "blue", mid = "gray", high = "red", midpoint = 15) + 
    geom_point() + 
    theme_bw()
  # ggsave("temperature.png")
```


Draw a world map with precipitation except over 4000 mm/yr (to avoid extended legend).

```{r precipitation}
climate %>%
  dplyr::filter(prec < 4000) %>%
  ggplot(aes(lon, lat, colour = prec)) +
    scale_colour_gradient2(low = "yellow", mid = "gray", high = "blue", midpoint = 1500) + 
    geom_point() + 
    theme_bw()
  # ggsave("precipitation.png")
```


Show relationships between temperature and precipitation except Japan.

```{r except_japan}
japan <- stringi::stri_unescape_unicode("\\u65e5\\u672c")
climate %>%
  dplyr::filter(country != japan) %>%
  ggplot(aes(temp, prec)) + 
  geom_point() + 
  theme_bw() + 
  theme(legend.position="none")
  # ggsave("climate_nojp.png")
```


Show relationships between temperature and precipitation including Japan.

```{r all_data}
climate %>%
  ggplot(aes(temp, prec)) + 
    geom_point() + 
    theme_bw()
  # ggsave("climate_all.png")
```


Show relationships between temperature and precipitation. 
Blue: Japan, red: others. 

```{r compare_japan}
climate %>%
  dplyr::mutate(jp = (country == japan)) %>%
  ggplot(aes(temp, prec, colour = jp)) + 
    geom_point() + 
    theme_bw() +
    theme(legend.position="none")
  # ggsave("climate_compare_jp.png")

```

## Citation

Toshikazu Matsumura (2022) Tools for download climate data from Japan Meteorological Agency with R. https://github.com/matutosi/clidatajp/.
